Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-10-25 ms/plosHIVcover_resubm.tex
update cover letter

We appreciate the opportunity to revise our manuscript.
In addition to extensive clarification and correction following
the reviewers' comments, we implemented a more complex model
that includes variation in contact rates among individuals.

\hrule

>>>>

We appreciate the opportunity to revise our manuscript.
In addition to extensive clarification and correction following
the reviewers' comments (see detailed response below), 
we have implemented an additional, more complex model
that includes heterogeneity in contact rates among individuals,
in order to address the reviewers' concern that we
did not look at a sufficiently realistic set of 
epidemiological models.

\vskip10pt
\hrule
